
Frie: hier wird es wahrscheinlich schwer die übung auf der platform direkt zu machen? 

ganz praktisch sehe ich schon die fragen nach Logo und CI kommen. latex und css sind natuerlich bitchesss aber how do we deal with this? :D bin kein fan davor, leute nicht zumindest vorzuwarnen, dass in der realität sowas auch noch auf sie zukommt. 

## Aufbau Video

1.  Kurze Einführung/Wiederholung was ist R-Markdown?

2.  Wofür ist es nützlich?

    1.  --\> unter anderem Reporting (Export Möglichkeiten von RMarkdown)
    2.  --\> Exercise 1: Explore R-Markdown Gallery, post your fav in slack channel

3.  Struktur von RMarkdown

    1.  YAML Header

    2.  Inhalte

    3.  Knitr Code Chunks

```{=html}
<!-- -->
```
4.  Inhalte

    1.  Überschriften
    2.  Text
    3.  Listen
    4.  Links
    5.  Bilder
    6.  --\> Exercise mit [Tutorial](https://commonmark.org/help/tutorial/)

5.  Code Chunks (wurde evtl schon abgedeckt?)

    1.  Tabellen einfügen
    2.  Plots darstellen

6.  YAML Header

    1.  Basic Funktionen

    2.  Advanced Optionen

    3.  Params Parameter

    4.  --\> Exercise wähle ein theme aus, füge ein Inhaltsverzeichnis ein, toggle sichtbarkeit von chunks

## Topic 1

### Exercise

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
