## Aufbau Video

1.  Recap letzter Woche?

2.  Parameter definieren

    1.  Radio Button

    2.  Liste

    3.  Range

3.  Parameter per Hand eingeben

4.  Parameter mit code "eingeben"

Frie: hier müsste man ggf. for loops einführen oder purrr::walk - das ist in den bisherigen lektionen noch nicht drin oder?

Frie: weiß nicht ob das zu weit geht und zu technisch wird aber was ist mit child documents? https://bookdown.org/yihui/rmarkdown-cookbook/child-document.html

## Topic 1

### Exercise

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
